Time-Series and Frequency-Series Features for Musical Instrument Classification

### 2020-06-10 Thesis/Classification Features/Time-Freq Features.tex
10 June 2020
- Updates to Feature Extraction paper

\paragraph*{}Additiona

@@

\begin{equation}
\label{IDFT}
S_{k} =  \frac{1}{N}\sum_{n=0}^{N-1} F_{n} \cdot e^{-2\pi i\frac{kn}{N}}
\end{equation}

@@

@@

\begin{algorithm}
\label{ESD}
\caption{Compute energy spectral density of banks in frequency space array $F$}
\begin{algorithmic}
\REQUIRE Discrete frequency series signal: $F$ of length $N$
\REQUIRE Array-like object: $x$, length $N$, maps each index of $F$ to a real-valued frequency bin.
\REQUIRE Array-like object: $P$, containing $k$ upper bound / lower bound pairs.
\REQUIRE Integration function, method or operation: \textit{INTG}

@@

\RETURN Bin\_ESDs

>>>>

@@

\begin{equation}
\label{IDFT}
S_{k} =  \frac{1}{N}\sum_{n=0}^{N-1} F_{n} \cdot e^{+2\pi i\frac{kn}{N}}
\end{equation}

@@

\paragraph*{}Due to the physical properties of various musical instruments, there are often times when overtones from a pitch are not present in a waveform or the presence is very minuscule when producing the frequency spectrum.

@@

\begin{algorithm}
\label{ESD}
\caption{Compute energy spectral density of banks in frequency space array $F$}
\begin{algorithmic}
\REQUIRE Discrete frequency series signal: $F$ of length $N$
\REQUIRE Array-like object: $x$, length $N$, maps each index of $F$ to a real-valued frequency bin.
\REQUIRE Array-like object: $P$, containing $k$ upper bound / lower bound pairs.
\REQUIRE Integration or summation function, method, or operation for array of discrete points: \textit{INTG}

@@

\RETURN Bin\_ESDs
\end{algorithmic}
\end{algorithm}

\paragraph*{}The resulting array of floating-point numbers gives the energy spectral density distribution of the waveform in that frame of time. By choosing frames boundaries:

\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
\textbf{Bounds} & 	\textbf{Bank 1} & \textbf{Bank 2} & \textbf{Bank 3} & \textbf{Bank 4} & 
					\textbf{Bank 5} & \textbf{Bank 6} & \textbf{Bank 7} & \textbf{Bank 8}  \\ \hline
\textbf{Low [Hz]}	& 0		& 32	& 64 & 128 & 256 & 512 & 1024 & 2048  		\\ 	\hline
\textbf{High [Hz]}	& 32	& 64	& 128 & 256 & 512 & 1024 &  2048 & 6000 	\\	\hline
\end{tabular}
\end{center}

These set of banks allow for a reasonable range such that every instrument contains at least one overtone in the frequency-spectrum for any given pitch played. This ESD distribution shows to be a valuable set of features for classification. Since this is largely what shapes human understanding of timbre, it is reasonable to use emphasise the importance of these features.
